`r paste(params$species)` climatic and biotic velocities for `r paste(params$region)` (immature: `r paste(params$immature)`

### 2020-07-09 analysis/VOCC/3-vocc-dist.Rmd
vocc based on ROMs

---
title: "`r paste(params$species)` climatic and biotic velocities for `r paste(params$region)` (immature: `r paste(params$immature)`"
author: "Philina English"
date: "`r Sys.Date()`"
output: html_document 
params: 
    # species: "Redbanded Rockfish"
    # species: "Widow Rockfish"
    # species: "Canary Rockfish"
    # species: "English Sole"
    # species: "Dover Sole"
    # species: "Flathead Sole"
    # species: "Sablefish"
    species: "Arrowtooth Flounder"
    immature: T
    # region: "West Coast Vancouver Island"
    # region: "both odd year surveys"
    region: "West Coast Haida Gwaii"
    covs: "-tv-depth-only"
    climate_mod: "2020-06-20-more2016"
    scrambled_years: FALSE
---

@@

#### Load climate data
```{r}
nd_all <- readRDS(paste0("data/predicted-DO-", climate_mod, ".rds")) %>% select(X, Y, year, temp, do_est)

@@

# temp_sd_choice <- temp_min_sd
# lower_change_t <- temp_sd_choice*2
# upper_change_t <- temp_sd_choice*2

>>>>

---
title: "`r paste(params$species)` climatic and biotic velocities for `r paste(params$region)` (immature: `r paste(params$immature)`"
author: "Philina English"
date: "`r Sys.Date()`"
output: html_document 
params: 
    # species: "Redbanded Rockfish"
    # species: "Widow Rockfish"
    # species: "Canary Rockfish"
    # species: "English Sole"
    # species: "Dover Sole"
    # species: "Flathead Sole"
    # species: "Sablefish"
    species: "Arrowtooth Flounder"
    immature: T
    region: "West Coast Vancouver Island"
    # region: "both odd year surveys"
    # region: "West Coast Haida Gwaii"
    covs: "-tv-depth-only"
    climate_mod: "2020-06-20-more2016"
    scrambled_years: FALSE
---

@@

#### Load climate data
```{r}
nd_all <- readRDS(paste0("data/predicted-DO-", climate_mod, "-roms.rds")) %>% select(X, Y, year, temp, do_est, roms_temp)

@@

# temp_sd_choice <- temp_min_sd
# lower_change_t <- temp_sd_choice*2
# upper_change_t <- temp_sd_choice*2
```

### Annual temperature (ROMS)
```{r}
rm(roms)
try({roms <- readRDS(paste0("data/_climate_vocc/annual-temp-vocc-", climate_mod, "-scale-", scale_fac, "-ssid", ssid_string, "-years-", years_sampled, ".rds"))
})

if(!exists("roms")){

roms <- vocc_gradient_calc(d, "roms_temp",
  scale_fac = scale_fac,
  # all layers with max indice will be averaged for spatial gradient
  # if default (NULL) will use all years
  indices = indices,
  # divisor = 1, #default of 10 gives per decade
  quantile_cutoff = 0.05
)

roms <- roms %>%
  mutate(
    ## these are only relevant if divisor = 1 
    # trend_per_year = trend,
    # trend_per_decade = trend_per_year * 10,
    trend_per_year = trend/10,
    trend_per_decade = trend_per_year * 10,
    velocity = velocity
  ) %>%
  dplyr::mutate(X = x, Y = y)

# # FULL DATASET
# # mean(roms$sd, na.rm = T) # [1] 0.3434
# # min(roms$sd, na.rm = T) # [1] 0.1266
# # max(roms$sd, na.rm = T) # [1] 1.12
# # median(roms$sd, na.rm = T) # [1] 0.287
# # 
# # 2008 DATASET
# mean(roms$sd, na.rm = T) # [1] 0.3274
# temp_min_sd <- min(roms$sd, na.rm = T) # [1] 0.1035
# max(roms$sd, na.rm = T) # [1] 1.248
# temp_median_sd <- median(roms$sd, na.rm = T) # [1] 0.2882
# 
# temp_sd_choice <- temp_min_sd
# lower_change_t <- temp_sd_choice*2
# upper_change_t <- temp_sd_choice*2
# 
# dvocc_t <- make_vector_data(d,
#   variable_names = c("temp"),
#   ssid = model_ssid,
#   input_cell_size = 2,
#   scale_fac = scale_fac,
#   min_dist = 0,
#   delta_t_total = years_sampled,
#   delta_t_step = 2,
#   indices = indices,
#   min_thresholds = lower_change_t,
#   max_thresholds = upper_change_t,
#   round_fact = 10
# )
# 
# dvocc_t <- dvocc_t %>% mutate(dvocc = if_else(slope < 0, -km_per_decade, km_per_decade), trend = slope)
# dvocc_t <- dvocc_t %>% mutate(dvocc = if_else(dvocc > (max_dist_all_years/ year_range)*10, 
#   (max_dist_all_years/ year_range)*10, dvocc))
# dvocc_t <- mutate(dvocc_t, dvocc = if_else(dvocc < -(max_dist_all_years / year_range)*10,
#   -(max_dist_all_years / year_range)*10, dvocc))
# 
# dv_t <- dvocc_t %>% select(icell, x, y, dvocc) %>% unique()
# 
# # glimpse(dv_t)
# # glimpse(roms)
# 
# # roms$dvocc <- dv_t$dvocc
# 
# roms <- left_join(roms, dv_t)

saveRDS(roms, file = paste0("data/_climate_vocc/annual-temp-vocc-", climate_mod, "-scale-", scale_fac, "-ssid", ssid_string, "-years-", years_sampled, ".rds"))

# mine <- gf2 %>% select(x, y, temp_trend = trend, temp_vel = velocity, temp_grad= gradient)
# other <- roms %>% select(x, y, roms_temp_trend = trend, roms_temp_vel = velocity, roms_temp_grad= gradient)
# 
# check <- left_join(mine, other)
# 
# ggplot(check, aes(roms_temp_trend, temp_trend)) + 
#   geom_point(alpha=0.2) +
#   coord_cartesian(xlim = c(-1,2.5), ylim = c(-1,2.5)) +
#   geom_abline(intercept = 0, slope = 1) +
#   gfplot::theme_pbs()

}
```

```{r}
# ggplot(check, aes(roms_temp_vel, temp_vel)) + 
#   geom_point(alpha=0.2) +
#   coord_cartesian(xlim = c(-20,80), ylim = c(-20,80)) +
#   geom_abline(intercept = 0, slope = 1) +
#   gfplot::theme_pbs()
```
